  \documentclass[11pt,a4paper,sans]{article}

% --- Packages ---
\usepackage[utf8]{inputenc}
\usepackage[margin=0.75in]{geometry}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{xcolor}

% --- Style Configuration ---
\definecolor{TeslaRed}{HTML}{E31937}
\urlstyle{same}
\hypersetup{colorlinks=true, urlcolor=black}

\titleformat{\section}{\large\bfseries\color{TeslaRed}}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{5pt}
\setlist[itemize]{noitemsep, topsep=0pt, leftmargin=1.5em}

\begin{document}
\pagestyle{empty}

% --- Header ---
\begin{center}
    {\Huge \textbf{Nuhu Divine Hyellafuda}} \\ [6pt]
    \small Ota, Ogun State, Nigeria $|$ +234 907 603 8686 \\
    \href{mailto:divine.nuhu25@gmail.com}{divine.nuhu25@gmail.com} \\
    \href{https://www.linkedin.com/in/divine-nuhu-21aa133b3}{linkedin.com/in/divine-nuhu-21aa133b3} $|$ \href{https://github.com/Divine-Nuhu-design}{github.com/Divine-Nuhu-design}
\end{center}

% --- Professional Summary ---
\section{PROFESSIONAL SUMMARY}
First-year Electrical \& Electronics Engineering student at Covenant University with a focused interest in Power Electronics and Machine Learning. Passionate about engineering sustainable solutions for Electric Vehicle (EV) technology. Committed to First Principles thinking and eager to apply emerging skills in simulation and AI to real-world energy challenges.

% --- Education ---
\section{EDUCATION}
\textbf{Covenant University} \hfill Ota, Nigeria \\
Bachelor of Engineering (B.Eng.) in Electrical \& Electronics Engineering \hfill Oct 2025 -- July 2030 (Expected)
\begin{itemize}
    \item \textbf{Relevant Coursework:} Engineering Mathematics, Applied Physics (Electricity \& Magnetism), Basic Electrical Circuits, Introduction to Computing, Technical Drawing.
\end{itemize}

\vspace{6pt}

\textbf{Great Faith International School} \hfill Port Harcourt, Nigeria \\
West African Senior School Certificate (WASSCE) \hfill 2019 -- 2025
\begin{itemize}
    \item Graduated with strong distinctions in Mathematics, Further Mathematics, and Physics.
\end{itemize}

% --- Technical Skills ---
\section{TECHNICAL SKILLS}
\textbf{Design \& Simulation:} MATLAB \& Simulink (In Progress), LTspice (In Progress), Circuit Design. \\
\textbf{Specialized Interest:} Power Electronics, EV Powertrain Systems, Renewable Energy. \\
\textbf{Tools \& Software:} Microsoft Office Suite (Advanced Word, Excel, PowerPoint). \\
\textbf{AI \& Machine Learning:} Currently undergoing Microsoft Training on ML and Artificial Intelligence.

% --- Projects ---
\section{ACADEMIC \& PERSONAL PROJECTS}
\textbf{EV Systems Modeling (Incoming)} \hfill Feb 2026 -- Present \\
\begin{itemize}
    \item Initiating simulation projects using \texttt{MATLAB} to model battery discharge cycles.
    \item Utilizing \texttt{LTspice} to design and analyze basic DC-DC converter circuits for power efficiency.
\end{itemize}

\vspace{4pt}

\textbf{AI Integration Study} \hfill Jan 2026 -- Present \\
\begin{itemize}
    \item Exploring the application of Machine Learning algorithms to optimize battery management systems (BMS).
\end{itemize}

% --- Soft Skills ---
\section{SOFT SKILLS \& CORE COMPETENCIES}
\begin{itemize}
    \item \textbf{Analytical:} Problem Solving, First Principles Analysis, Critical Thinking.
    \item \textbf{Operational:} Time Management, Ability to Work Under Pressure, Multitasking, Team Collaboration.
\end{itemize}

% --- Interests & Languages ---
\section{INTERESTS \& LANGUAGES}
\begin{itemize}
    \item \textbf{Interests:} Robotics, STEM Competitions, Chess (Strategy), Tech Articles.
    \item \textbf{Languages:} English (Native/Professional), French (Elementary).
\end{itemize}

\end{document}